---
title: "fl1"
format: html
editor: visual
---
#install packages
```{r}
install.packages(c("tidyverse", "readxl", "janitor", "here"))
install.packages(c("cars", "effectsize", "rstatix"))
install.packages("sjmisc")
install.packages("writexl")
install.packages("paletteer")
```


#packages
```{r}
#| message: false
# general use
library(tidyverse)
library(readxl)
library(here)
library(janitor)
library(car) # levene test
library(effectsize) # assess effect size 
library(rstatix) # anova, kruskal wallis
library(sjmisc)
library(writexl)
library(paletteer)
```

#June FL1 Read Data - TEST
```{r}
fl1_june <- read_xlsx(path = here("data", "june 2026 firebreak, aidan copy 1.xlsx"),
                      sheet = "FL1")

fl1s_june <- read_xlsx(path = here("data", "june 2026 firebreak, aidan copy 1.xlsx"),
                      sheet = "FL1S")

fl1n_june <- read_xlsx(path = here("data", "june 2026 firebreak, aidan copy 1.xlsx"),
                      sheet = "FL1N")

```

#June FL1 Wrangling - TEST
```{r}
fl1_june_clean <- fl1_june %>% 
  slice(-81) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words 
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "flat", orientation = "central") %>% 
  drop_na(cover) #remove all species not observed

fl1s_june_clean <- fl1s_june %>% 
   drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "flat", orientation = "south") %>% 
  drop_na(cover) #remove all species not observed

fl1n_june_clean <- fl1n_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "flat", orientation = "north") %>% 
  drop_na(cover) #remove all species not observed

fl1_full <- merge_df(fl1_june_clean, fl1s_june_clean, fl1n_june_clean) #merge all fl1 dfs
```



#June Data Read In
```{r}
#Staging Area 1
sa1_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA1")

sa1s_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA1S")

sa1n_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA1N")

#Flat 1
fl1_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "FL1")

fl1s_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "FL1S")

fl1n_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "FL1N")

#Slope 1
sl1_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SL1")

sl1w_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SL1W")

sl1e_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SL1E")

#Staging Area 2
sa2_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA2")

sa2s_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA2S")

sa2n_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA2N")

#Flat 2
fl2_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "FL2")

fl2w_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "FL2W")

fl2e_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "FL2E")

#Slope 2
sl2_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SL2")

sl2n_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SL2N")

sl2s_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SL2S")

#Staging Area 3
sa3_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA3")

sa3e_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA3E")

sa3w_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA3W")

#Flat 3
#fl3_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      #sheet = "FL3")

#fl3e_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      #sheet = "FL3E")

#fl3w_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      #sheet = "FL3W")

#Slope 3
sl3_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SL3")

sl3w_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SL3W")

sl3e_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SL3E")

#Staging Area 4
sa4_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA4")

sa4e_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      sheet = "SA4E")

#no SA4N due to STIPA planting in January

#Staging Area 6
#sa6_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      #sheet = "SA6")

#sa6e_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      #sheet = "SA6E")

#sa6w_june <- read_xlsx(path = here("data", "FirebreakData2026_final.xlsx"),
                      #sheet = "SA6W")
```

#June Wrangling
```{r}
#Staging Area 1 Wrangling
sa1_june_clean <- sa1_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "staging area", orientation = "central", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa1s_june_clean <- sa1s_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "staging area", orientation = "south", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa1n_june_clean <- sa1n_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "staging area", orientation = "north", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa1_full <- merge_df(sa1_june_clean, sa1s_june_clean, sa1n_june_clean)

#Flat 1 Wrangling
fl1_june_clean <- fl1_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "flat", orientation = "central", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl1s_june_clean <- fl1s_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "flat", orientation = "south", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl1n_june_clean <- fl1n_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "flat", orientation = "north", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl1_full <- merge_df(fl1_june_clean, fl1s_june_clean, fl1n_june_clean)

#Slope 1 Wrangling
sl1_june_clean <- sl1_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "slope", orientation = "central", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl1e_june_clean <- sl1e_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "slope", orientation = "east", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl1w_june_clean <- sl1w_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "slope", orientation = "west", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl1_full <- merge_df(sl1_june_clean, sl1e_june_clean, sl1w_june_clean)

#Staging Area 2 Wrangling
sa2_june_clean <- sa2_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "staging area", orientation = "central", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa2s_june_clean <- sa2s_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "staging area", orientation = "south", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa2n_june_clean <- sa2n_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "staging area", orientation = "north", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa2_full <- merge_df(sa2_june_clean, sa2s_june_clean, sa2n_june_clean)

#Flat 2 Wrangling
fl2_june_clean <- fl2_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "flat", orientation = "central", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl2e_june_clean <- fl2e_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "flat", orientation = "east", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl2w_june_clean <- fl2w_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "flat", orientation = "west", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl2_full <- merge_df(fl2_june_clean, fl2e_june_clean, fl2w_june_clean)

#Slope 2 Wrangling
sl2_june_clean <- sl2_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "slope", orientation = "central", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl2n_june_clean <- sl2n_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "slope", orientation = "north", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl2s_june_clean <- sl2s_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "slope", orientation = "south", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl2_full <- merge_df(sl2_june_clean, sl2n_june_clean, sl2s_june_clean)

#Staging Area 3 Wrangling
sa3_june_clean <- sa3_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "staging area", orientation = "central", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa3e_june_clean <- sa3e_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "staging area", orientation = "east", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa3w_june_clean <- sa3w_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "staging area", orientation = "west", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa3_full <- merge_df(sa3_june_clean, sa3e_june_clean, sa3w_june_clean)

#Flat 3 Wrangling - not collected yet


#Slope 3 Wrangling
sl3_june_clean <- sl3_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "slope", orientation = "central", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl3e_june_clean <- sl3e_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "slope", orientation = "east", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl3w_june_clean <- sl3w_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "slope", orientation = "west", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl3_full <- merge_df(sl3_june_clean, sl3e_june_clean, sl3w_june_clean)

#Staging Area 4 Wrangling
sa4_june_clean <- sa4_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 4, aspect = "staging area", orientation = "central", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa4e_june_clean <- sa4e_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 4, aspect = "staging area", orientation = "east", month = "June", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa4_full <- merge_df(sa4_june_clean, sa4e_june_clean)

#Staging Area 6 - not collected yet
```


#June Full Species List
```{r}
june <- merge_df(fl1_full, fl2_full, sa1_full, sa2_full, sa3_full, sa4_full, sl1_full, sl2_full, sl3_full) #merge all june dfs

all_june <- june %>%
  mutate(status = case_when(
    site == 1 & aspect == "slope" ~ "Slope 1",
    site == 1 & aspect == "flat" ~ "Flat 1",
    site == 1 & aspect == "staging area" ~ "Staging Area 1",
    site == 2 & aspect == "slope" ~ "Slope 2",
    site == 2 & aspect == "flat" ~ "Flat 2",
    site == 2 & aspect == "staging area" ~ "Staging Area 2",
    site == 3 & aspect == "slope" ~ "Slope 3",
    site == 3 & aspect == "staging area" ~ "Staging Area 3",
    site == 4 & aspect == "staging area" ~ "Staging Area 4",
    .default = "Other")) #new column for each site

species_list <- june %>% dplyr::select(species) %>% distinct() #create list of all individual species

write_xlsx(species_list, "species_list_june.xlsx") #export list, classified in excel

species_class_june <- read_xlsx(path = here("data", "species_june_classified.xlsx")) #read in classified df

all_june_classified <- merge(all_june, species_class_june, by = "species") %>% 
  mutate(species = case_when(
             species == "ERO Spp" ~ "ERO spp",
             species == "PLATIN" ~ "PLATEN",
             species == "PLANTIN" ~ "PLATEN",
             species == "LUPspp." ~ "LUP spp",
             species == "UNK ERI" ~ "UNKERI",
             species == "CALWEE" ~ "PAECAL",
             species == "STEUIR" ~ "STEVIR",
             .default = species)) #rename mistakes in entered data
```

#June Plotting N/NN - TEST
```{r}
ggplot(all_june_classified) +
  aes(y = (as.numeric(as.character(cover))), x = status, color = class ) +
  geom_boxplot() +
  facet_wrap(~status, ncol = 3, scales = "free") +
  #geom_point(position=position_jitterdodge(
 #  jitter.width = 0,
 #  jitter.height = 0,
 #   seed = NULL),
  #          alpha = 0.3) +
  scale_color_manual(values = c("#e52e39", "#FFBF00", "#3271a5")) +
  labs(x = "Aspect",
       y = "Cover",
       color = "Cover Type") +
  theme_minimal()
```


#Nov Data Read In
```{r}
#Staging Area 1
sa1_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA1")

sa1s_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA1S")

sa1n_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA1N")

#Flat 1
fl1_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "FL1")

fl1s_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "FL1S")

fl1n_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "FL1N")

#Slope 1
sl1_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SL1")

sl1w_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SL1W")

sl1e_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SL1E")

#Staging Area 2
#sa2_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      #sheet = "SA2")

#sa2s_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      #sheet = "SA2S")

#sa2n_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      #sheet = "SA2N")

#Flat 2
fl2_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "FL2")

fl2w_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "FL2W")

fl2e_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "FL2E")

#Slope 2
sl2_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SL2")

sl2n_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SL2N")

sl2s_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SL2S")

#Staging Area 3
sa3_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA3")

sa3e_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA3E")

sa3w_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA3W")

#Flat 3
fl3_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "FL3")

fl3e_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "FL3E")

fl3w_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "FL3W")

#Slope 3
sl3_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SL3")

sl3w_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SL3W")

sl3e_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SL3E")

#Staging Area 4
sa4_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA4")

sa4e_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA4E")

sa4n_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA4N")

#Staging Area 6
sa6_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA6")

sa6e_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA6E")

sa6w_nov <- read_xlsx(path = here("data", "FirebreakData_Nov2026.xlsx"),
                      sheet = "SA6W")
```

#Nov Wrangling
```{r}
#Staging Area 1 Wrangling
sa1_nov_clean <- sa1_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "staging area", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa1s_nov_clean <- sa1s_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "staging area", orientation = "south", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  
  
sa1n_nov_clean <- sa1n_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "staging area", orientation = "north", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa1_full_nov <- merge_df(sa1_nov_clean, sa1s_nov_clean, sa1n_nov_clean)

#!!!!!!!!!!!!!!!!!!!!!!!!!!!! ADD MONTH & YEAR HERE !!!!!!!!!!!!!!!!!!!!!!!!!!!!!

#Flat 1 Wrangling
fl1_nov_clean <- fl1_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "flat", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl1s_nov_clean <- fl1s_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "flat", orientation = "south", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl1n_nov_clean <- fl1n_june %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "flat", orientation = "north", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl1_full_nov <- merge_df(fl1_nov_clean, fl1s_nov_clean, fl1n_nov_clean)

#Slope 1 Wrangling
sl1_nov_clean <- sl1_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "slope", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl1e_nov_clean <- sl1e_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "slope", orientation = "east", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl1w_nov_clean <- sl1w_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 1, aspect = "slope", orientation = "west", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl1_full_nov <- merge_df(sl1_nov_clean, sl1e_nov_clean, sl1w_nov_clean)

#Staging Area 2 Wrangling - lost datasheet

#Flat 2 Wrangling
fl2_nov_clean <- fl2_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "flat", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl2e_nov_clean <- fl2e_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "flat", orientation = "east", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl2w_nov_clean <- fl2w_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "flat", orientation = "west", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl2_full_nov <- merge_df(fl2_nov_clean, fl2e_nov_clean, fl2w_nov_clean)

#Slope 2 Wrangling
sl2_nov_clean <- sl2_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "slope", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl2n_nov_clean <- sl2n_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "slope", orientation = "north", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl2s_nov_clean <- sl2s_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 2, aspect = "slope", orientation = "south", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl2_full_nov <- merge_df(sl2_nov_clean, sl2n_nov_clean, sl2s_nov_clean)

#Staging Area 3 Wrangling
sa3_nov_clean <- sa3_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "staging area", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa3e_nov_clean <- sa3e_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "staging area", orientation = "east", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa3w_nov_clean <- sa3w_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "staging area", orientation = "west", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa3_full_nov <- merge_df(sa3_nov_clean, sa3e_nov_clean, sa3w_nov_clean)

#Flat 3 Wrangling
fl3_nov_clean <- fl3_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "flat", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl3e_nov_clean <- fl3e_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "flat", orientation = "east", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl3w_nov_clean <- fl3w_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "flat", orientation = "west", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

fl3_full_nov <- merge_df(fl3_nov_clean, fl3e_nov_clean, fl3w_nov_clean)

#Slope 3 Wrangling
sl3_nov_clean <- sl3_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "slope", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl3e_nov_clean <- sl3e_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "slope", orientation = "east", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl3w_nov_clean <- sl3w_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 3, aspect = "slope", orientation = "west", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sl3_full_nov <- merge_df(sl3_nov_clean, sl3e_nov_clean, sl3w_nov_clean)

#Staging Area 4 Wrangling
sa4_nov_clean <- sa4_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 4, aspect = "staging area", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa4e_nov_clean <- sa4e_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 4, aspect = "staging area", orientation = "east", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa4n_nov_clean <- sa4n_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 4, aspect = "staging area", orientation = "north", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed

sa4_full_nov <- merge_df(sa4_nov_clean, sa4e_nov_clean, sa4n_nov_clean)

#Staging Area 6
sa6_nov_clean <- sa6_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 6, aspect = "staging area", orientation = "central", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa6e_nov_clean <- sa6e_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 6, aspect = "staging area", orientation = "east", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed  

sa6w_nov_clean <- sa6w_nov %>% 
  drop_na(Species) %>% # remove n/a row
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% #name rows with values from row 1 (species)
  rownames_to_column() %>% 
  mutate(rowname = case_when(grepl("No.", rowname) ~ "Number",
                           grepl("Cov.", rowname) ~ "Cover")) %>% #rename values to regular words
  pivot_longer(cols = ACMAME:HIRINC,
              names_to = "species",
              values_to = "values") %>% #elongate df with species as values, not columns
  pivot_wider(names_from = "rowname",
              values_from = "values") %>% #create columns for number and cover
  clean_names() %>% 
  rename(strip = strip_no,
         quad = quad_no) %>% 
  mutate(site = 6, aspect = "staging area", orientation = "west", month = "November", year = "2026") %>% 
  drop_na(cover)  #remove all species not observed

sa6_full_nov <- merge_df(sa6_nov_clean, sa6e_nov_clean, sa6w_nov_clean)
```


#November Species List
```{r}
nov <- merge_df(fl1_full_nov, fl2_full_nov, fl3_full_nov, sa1_full_nov, sa6_full_nov, sa3_full_nov, sa4_full_nov, sl1_full_nov, sl2_full_nov, sl3_full_nov) #merge all nov data

all_nov <- nov %>%
  mutate(status = case_when(
    site == 1 & aspect == "slope" ~ "Slope 1",
    site == 1 & aspect == "flat" ~ "Flat 1",
    site == 1 & aspect == "staging area" ~ "Staging Area 1",
    site == 2 & aspect == "slope" ~ "Slope 2",
    site == 2 & aspect == "flat" ~ "Flat 2",
    site == 6 & aspect == "staging area" ~ "Staging Area 6",
    site == 3 & aspect == "slope" ~ "Slope 3",
    site == 3 & aspect == "flat" ~ "Flat 3",
    site == 3 & aspect == "staging area" ~ "Staging Area 3",
    site == 4 & aspect == "staging area" ~ "Staging Area 4",
    .default = "Other")) #new column for each site

species_list_nov <- nov %>% dplyr::select(species) %>% distinct() #create list of all individual species

write_xlsx(species_list_nov, "species_list_nov.xlsx") #export list, classified in excel

species_class_nov <- read_xlsx(path = here("data", "species_list_nov_classified.xlsx")) #read in classified df

all_nov_classified <- merge(all_nov, species_class_nov, by = "species") %>% 
    mutate(species = case_when(
             species == "LUP sp." ~ "LUP spp",
             species == "LUP Sp." ~ "LUP spp",
             .default = species)) #fix mistakes
```

#Comparison Nov/June
```{r}
all_all <- merge_df(all_nov_classified, all_june_classified) %>% #merge nov and june
   mutate(class = case_when(
    class == "native" ~ "Native",
    class == "non-native" ~ "Non-Native", #rename classification for figures
    class == "bare ground" ~ "Bare Ground")) %>% 
  dplyr::mutate(month = fct_relevel(month, "November", "June"),
                class = fct_relevel(class, "Native", "Non-Native", "Bare Ground")) #reorder months and class for figures

all_sumcover <- all_all %>% group_by(year, month, status, orientation, strip, quad, class) %>% summarise(sumcover = sum(as.numeric(as.character(cover)))) #summarized cover for native, non-native, bare ground across quads at each site (everything in group_by)
```

#Figures - Sum Cover
```{r}
sa4_sumcover <- all_sumcover %>%  filter(status == "Staging Area 4") #filter for site

ggplot(sa4_sumcover) +
  aes(y = sumcover, x = class, color = class) +
  geom_boxplot() +
  facet_wrap(~month, scales = "fixed") +
  #geom_point(position=position_jitterdodge(
  # jitter.width = 0,
  # jitter.height = 0,
   # seed = NULL),
   # alpha = 0.3) +
  scale_color_manual(values = c("#38A800", "#e52e39", "#888")) +
  labs(x = NULL,
       y = "Cover") +
  ggtitle("Staging Area 4") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position = "none")
```

#Figures - Most Abundant NN Species
```{r}
nn_cover <- all_all %>% filter(class == "Non-Native") %>% group_by(status, month, species) %>% 
  summarise(nncover = sum(as.numeric(as.character(cover)))) #summarize nonnative cover across each site per species

nn_sum_cover <- nn_cover %>% group_by(status, month) %>% summarise(sum_cover = sum(nncover)) #total sum of nn cover per site

nonnative_cover <- merge(nn_cover, nn_sum_cover) %>% mutate(cover_ratio = (as.numeric(as.character(nncover))/sum_cover)*100) #merge dfs, create new column of % of nn cover per species per site

nn_species_list <- all_all %>% filter(class == "Non-Native") %>% dplyr::select(species) %>%  distinct() #checking for all distinct nn species

nn_sa4 <- nonnative_cover %>% filter(status == "Staging Area 4") #filter by site

ggplot(nn_sa4) +
  aes(x = month, y = cover_ratio, fill = species) +
  geom_col()  + 
  scale_fill_paletteer_d("rcartocolor::Vivid") +
  labs(x = NULL,
       y = "% of Non-Native Cover",
       fill = "Species") +
  ggtitle("Staging Area 4") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

```

#Figures - Most Abundant NN Species, No Annual Grass
```{r}
nn_cover_noAG <- all_all %>% filter(class == "Non-Native") %>% filter(!species == "ANNGRS") %>% group_by(status, month, species) %>% summarise(nncover = sum(as.numeric(as.character(cover)))) ##summarize nonnative cover across each site per species, minus annual grass

nn_sum_cover_noAG <- nn_cover %>% filter(!species == "ANNGRS") %>% group_by(status, month) %>% summarise(sum_cover = sum(nncover)) #total sum of nn cover per site minus annual grass

nonnative_cover_noAG <- merge(nn_cover_noAG, nn_sum_cover_noAG) %>% mutate(cover_ratio = (as.numeric(as.character(nncover))/sum_cover)*100) #merge dfs, create new column of % of nn cover per species per site

nn_sa4_noAG <- nonnative_cover_noAG %>% filter(status == "Staging Area 4") #filter by site

ggplot(nn_sa4_noAG) +
  aes(x = month, y = cover_ratio, fill = species) +
  geom_col()  + 
  scale_fill_paletteer_d("tidyquant::tq_dark") +
  labs(x = NULL,
       y = "% of Non-Native Cover (-ANNGRS)",
       fill = "Species") +
  ggtitle("Staging Area 4") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

#Figures - Most Abundant Native Species
```{r}
n_cover <- all_all %>% filter(class == "Native") %>% group_by(status, month, species) %>% 
  summarise(ncover = sum(as.numeric(as.character(cover)))) #summarize native cover across each site per species

view(n_species_list)

n_sum_cover <- n_cover %>% group_by(status, month) %>% summarise(sum_cover = sum(ncover)) #total sum of n cover per site

native_cover <- merge(n_cover, n_sum_cover) %>% mutate(cover_ratio = (as.numeric(as.character(ncover))/sum_cover)*100) #merge dfs, create new column of % of n cover per species per site

n_species_list <- all_all %>% filter(class == "Native") %>% dplyr::select(species) %>%  distinct() #checking for all distinct n species

n_sl2 <- native_cover %>% filter(status == "Slope 2") #filter by site

ggplot(n_sl2) +
  aes(x = month, y = cover_ratio, fill = species) +
  geom_col()  + 
  scale_fill_manual(values = c("#FAAA78", "#D94118", "#9EABEB", "#DE5997", "#7FC98E", "#E36F6F", "#5484CC", "#ADAB28", "#63BC15", "#C487E6", "#E89E27", "#A623AD",  "#71C716", "#57BFD6", "#F2C469", "#826BC9", "#A47DB0")) +
  labs(x = NULL,
       y = "% of Native Cover",
       fill = "Species") +
  ggtitle("Slope 2") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) 

view(n_sl2)

#CLASSIFY ALL NATIVES AS ANNUAL OR PERRENIAL AND FILTER OUT ANNUALS, CREATE BAR CHART FOR ONLY CSS PERRENIALS!!!!!!

```

```{r} 
ACMAME "#FAAA78", ACMGLA "#D94118", CALMAC "#9EABEB", CALSPL "#DE5997", CROSET "#7FC98E", ERIFAS "#E36F6F", ERIFOL "#EB923F", GALANG "#5484CC", HEMFAS "#F0D30C", HOLVIR "#63BC15", JEPPAR "#806CEF", LESFIL "#C487E6", MADELE "#E89E27", NASPUL "#A623AD", PHACIC "#E79EEB", PLATEN "#9EEBE8", PSUCAL "#F2C469", STEVIR "#A47DB0", ARTCAL "#B4E0B8", CIROCC "#C7589E", DAUPUS "#C6620C", LUPSPP "#7B5182", LUPALB "#BF95C6", MADGRA "#C79D16", MALLAU "#931910", OPULIT "#71C716", SALAPI "#B6F0D9", SALMEL "#826BC9", UNKERI "#44BBB9", SOLDOU "#5B2663", BACPIL "#266335", ERICAN "#EBE9BE", ERIPAR "#D9AA75", BRICAL "#2DA474", PAECAL "#99205A", RAFCAL "#D1C5ED", MARMAC "#71BF79", LAYCON "#7CA758", HETGRA "#BCE41B", HETARB "#F5490A", EUCCHR "#0AB6F5", CORRIG "#055471", PSUCAN "#E07EA8", PSUBIO "#57BFD6", ISOMEN "#ADAB28"
```

